City traffic, IoT and Blockchain technologies

### 2020-10-25 thesis/report2.tex
Another paragraph.

>>>>

    Data assurance and resilience are two themes within the wide concept of Blockchain security. In \cite{TowardsdatAassuranceAndResilience} the authors are describing a communication mechanism for drones that achieves few objectives like trusted data origin (allows to know for sure which drone send a part of data), instant and permanent data integrity (data which the drones are reporting), trusted accountability (each command is recorded and malicious activities can be tracked down to the entities which started them) and resilient backend (nodes can go down or can start to behave weirdly with minimum distruption to others). The paper is especially interesting because it proposes a system which resembles ours. A swarm of devices (drones in the paper's case, cars in ours; cluster of drones and cluster or cities of cars) is a similar concept. A database separated from the blockchain, each part with its specific roles, is another similar concept. Nevertheless there are few differences. First and foremost the the Control System give drones a path where they should go on while the Cloud Server can augment the path with intelligent algorithms. On this thesis the application models the control as being exclusive the role of the actor. No central server, being a cloud or an intermediary block chain node, can give instructions to an actor. This doesn't mean the actor has the freedom and flexibility in doing everything it wants. But more on this in the next chapters.
